%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

	 \resumeProjectHeading
	{\textbf{Round-Trip Time Measurement in FABRIC} \emph{Master's Research Project}}{Sept 2023 - Nov 2023}
	\resumeItemListStart
	\resumeItem { Researched and analyzed RTT within the FABRIC testbed to evaluate network performance and user experience.}
	\resumeItem{Implemented and compared various RTT measurement methods, including One-way Latency with Precision Time Protocol, P4-based data plane monitoring, and TCP traffic analysis using Scapy.}
	\resumeItem { Designed and executed experiments on the FABRIC testbed, utilizing its high-speed optical connections and distributed infrastructure with help of multi-threaded scripts.}
	\resumeItemListEnd
	
    \resumeProjectHeading
    {\textbf{Modelling Illustrations using Generative Adversarial Nets} \emph{Bachelor's Capstone Project}}{Jan 2021 - July 2021}
    \resumeItemListStart
        \resumeItem { Designed and implemented a Deep Convolutional GAN architecture for generating anime character faces. Customized the SRResNet generator architecture by integrating 16 ResBlocks and sub-pixel CNNs, and designed a 10 ResBlock discriminator.}
        \resumeItem{ Built a dataset of approximately 143,000 anime faces by web-scraping with gallery-dl and employed python-animeface for face detection and preprocessing.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Image Super Pixelation using AI} \emph{}}{}
    \resumeItemListStart
        \resumeItem{ Developed a GAN-based solution for SISR, leveraging deep learning techniques to generate high-resolution images from low-resolution inputs with an upscaling factor of 4x. }
    \resumeItemListEnd
    
    
\iffalse
    \resumeProjectHeading
    {\textbf{CAPTCHA Recognization and Solving using CNN} \emph{}}{}
    \resumeItemListStart
        \resumeItem{Implemented Convolutional Neural Networks for recognition and resolution of Captcha images utilizing TensorFlow and OpenCV.}
    \resumeItemListEnd
\fi
\resumeSubHeadingListEnd